Using reference models in variable selection \vspace{.1in}

### 2020-05-02 paper/ref_approach.tex
modified first page for submission

>>>>

\vspace{2cm}

\textbf{Keywords}: variable selection, projection predictive approach, reference model

\textbf{Corresponding author}: Federico Pavone (\texttt{federicopavone01@gmail.com})

\textbf{Declarations}:
\begin{itemize}
\item \textbf{Funding}: Academy of Finland (grants 298742, and 313122), Finnish Center for Artificial Intelligence and Technology Industries of Finland Centennial Foundation (grant 70007503; Artificial Intelligence for Research and Development)

\item \textbf{Conflicts of interest/Competing interests}: no conflicts of interest

\item \textbf{Availability of data and material}: data and material available at \url{https://github.com/fpavone/ref-approach-paper}

\item \textbf{Code availability}: code available at \url{https://github.com/fpavone/ref-approach-paper}
\end{itemize}

\newpage
